### 2013-09-15 results.tex
total prostate axis comparisons b/w MR, ARFI and PATH

@@

>>>>

While difficult to compare the absolute lengths of the major and minor
anatomical axes of the prostates between the imaging modalities and pathology
due to different geometric distortions during imaging and changes to the organ
after excision, measurements of the prostate dimensions along the three
standard anatomic axes (apex-to-base, lateral-to-lateral, and
anterior-to-posterior) were made (Table~\ref{tab:mr_arfi_axes}), and the
relative ratios of the axes in imaging and pathology for the total prostate
volume were compared (Figure~\ref{fig:mr_arfi_total_axes}), and the relative
ratios of the central gland / zone anatomy were compared for MR and ARFI
imaging (Figure~\ref{fig:mr_arfi_central_axes}).

@@

\input{fig_mr_arfi_total_axes}
